---
title: "R Notebook"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

## **Palmer Penguins Dataset**

The **`palmerpenguins`** dataset has become a popular alternative to the
widely-used **`iris`** dataset for data visualization and teaching
statistical concepts.

### **Variables:**

1.  **species**:

    -   **Type**: Factor

    -   **Levels**:

        -   Adelie

        -   Chinstrap

        -   Gentoo

2.  **island**:

    -   **Type**: Factor

    -   **Levels**:

        -   Biscoe

        -   Dream

        -   Torgersen

3.  **bill_length_mm**:

    -   **Type**: Numeric

    -   **Description**: Length of the penguin's bill in millimeters.

4.  **bill_depth_mm**:

    -   **Type**: Numeric

    -   **Description**: Depth of the penguin's bill in millimeters.

5.  **flipper_length_mm**:

    -   **Type**: Numeric

    -   **Description**: Length of the penguin's flippers in
        millimeters.

6.  **body_mass_g**:

    -   **Type**: Numeric

    -   **Description**: Penguin's body mass in grams.

7.  **sex**:

    -   **Type**: Factor

    -   **Description**: Sex of the penguin.

8.  **year**:

    -   **Type**: Integer

    -   **Description**: Year of observation.

### **Usage in R:**

To use the dataset in R, follow the steps:

```{r}
install.packages("palmerpenguins")
library(palmerpenguins)
data("penguins")
head(penguins)
```

### **Advantages of Using `palmerpenguins` over `iris`:**

-   **Diversity of Data Types**: The dataset includes continuous,
    categorical, and ordinal variables.

-   **Missing Data**: Contains some missing values, making it
    representative of real-world datasets.

-   **Ethical Considerations**: Avoids controversies associated with
    Ronald A. Fisher and the **`iris`** dataset.

-   **Engagement**: Penguins are engaging and charismatic!

## Plotting in R Notebook

Let us create the same plot we did in the Simple R Script few days ago.

```{r}
install.packages("tidyverse")
library(ggplot2)

ggplot(
  data = penguins,
  mapping = aes(x = flipper_length_mm,
                y = body_mass_g,
                color = species)
) +
  geom_point()
```

## TODO

Please save your updates and Preview it.
